---
title: "DDP_Ass2_MyLeaflet"
author: "Loc Nguyen"
date: '2022-07-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

For further detail: <https://www.coursera.org/learn/data-products/peer/NLn0H/r-markdown-and-leaflet>


## Review criteria

**1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?**

I created this assignment on

```{r created_date}
Sys.Date()
```

**2. Does the web page feature an interactive map that appears to have been created with Leaflet?**

I show in map where I lived, studied and worked in Vietnam, my beloved country.

```{r interactive_map}
library(leaflet)
my_map <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=10.76868, lng=106.66698, popup="My Office") %>%
  addMarkers(lat=10.768057270983787, lng=106.69424047008869, popup="My Home") %>%
  addMarkers(lat=10.871153329747369, lng=106.77822308965327, popup="My School");
my_map

```
And I make some custom markers for more interesting.
```{r custom_marker}

office <- makeIcon(
iconUrl = "https://www.freeiconspng.com/uploads/office-icon--insharepics-11.png",
iconWidth = 31*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2, iconAnchorY = 16);

home <- makeIcon(
iconUrl = "https://www.freeiconspng.com/uploads/address-building-company-home-house-office-real-estate-icon--10.png",
iconWidth = 31*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2, iconAnchorY = 16);

school <- makeIcon(
iconUrl = "https://www.freeiconspng.com/uploads/school-icon-png-7.png",
iconWidth = 31*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2, iconAnchorY = 16);

my_map <- clearMarkers(my_map) %>%
  addMarkers(lat=10.76868, lng=106.66698, popup="My Office", icon = office) %>%
  addMarkers(lat=10.768057270983787, lng=106.69424047008869, popup="My Home", icon = home) %>%
  addMarkers(lat=10.871153329747369, lng=106.77822308965327, popup="My School", icon = school);

my_map
```
