---
title: "Tooth Growth Data Analysis"
author: "Loc Nguyen"
date: "9/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

- Load the ToothGrowth data and perform some basic exploratory data analyses  
- Analyze the ToothGrowth data by summary, visualization, statistics,...


## Loading libraries

Loading necessary libraries for the report


```{r libraries, results='hide', warning=FALSE,message=FALSE}
library(tidyverse)
library(ggplot2)
library(datasets)     
```

## Load the ToothGrowth data and perform some basic exploratory data analyses
### Load data
```{r load data}
data(ToothGrowth)
head(ToothGrowth)
```
### Perform some basic exploratory data analyses  
Comparing the data sets. Some plots to explore data 
```{r exploratory data}
ggplot(data=ToothGrowth, aes(x= supp, y = len,fill = supp)) +
      geom_boxplot() +
      facet_grid(.~dose) +
      ggtitle("Tooth Length by Dose (in milligrams/day) and Suplement Type")
```

## Provide a basic summary of the data.
Number of observations for each treatment/experiment. Total guinea pigs = 60

```{r table}
table(ToothGrowth$supp, ToothGrowth$dose)
```

Summarize data

```{r summary}
str(ToothGrowth)
summary(ToothGrowth)
```

## Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
The data contains: tooth length, supplement, and supplement dose for a group of guinea pigs. Presumably the data was not collected in a pairwise fashion. Performing T Test for each subset of data separated by dosages where the null hypothesis is that the tooth growth means of the two supp types

### Assumptions
- Samples are both unpaired and unequal variances  
- The sample population distribution is mound shaped and not skewed

### Test
Subset data by each value of dosage
```{r subset}
d.5 <- filter(ToothGrowth, dose == 0.5)
d1 <- filter(ToothGrowth, dose == 1)
d2 <- filter(ToothGrowth, dose == 2)
```

Test for dosage = 0.5

```{r}
test.5 <- t.test(len ~ supp, paired = FALSE, var.equal = FALSE, data = d.5)
test.5
```

Test for dosage = 1

```{r}
test1 <- t.test(len ~ supp, paired = FALSE, var.equal = FALSE, data = d1)
test1
```

Test for dosage = 2
```{r}
test2 <- t.test(len ~ supp, paired = FALSE, var.equal = FALSE, data = d2)
test2
```

### Conclusions
P-values are lower than 0.05 for dose 0.5 (`r test.5$p.value`) and 1.0 (`r test1$p.value`) but greater than for 2.0 (`r test2$p.value`).   
  
    
**We can say the supplements have different effects for dosages 0.5 and 1.0 but there is not enough evidence to prove so when the dosage is 2.0.**