---
title: "DDP | W3 Assignment"
author: "Loc Nguyen"
date: '2022-07-13'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Objectives

- Create a web page presentation using R Markdown that features a plot created with Plotly. 
- Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

For further detail: <https://www.coursera.org/learn/data-products/peer/a1Uy9/r-markdown-presentation-plotly>

## Review criteria

- Does the web page feature a date and is this date **less than two months** before the date that you're grading this assignment?

- Is the web page a presentation and does it feature an **interactive plot** that appears to have been created with *Plotly*?

## Description

- In this report, I will plot prices and carat (from 2 to 3 carat) of diamonds by scatterplot. And color will be identified by diamonds' quality. 
- About data, I used Diamonds dataset, which contains the prices and other attributes of almost 54,000 diamonds. For further detail, you can access <https://ggplot2.tidyverse.org/reference/diamonds.html>

## Created date
I created this assignment on

```{r created_date}
Sys.Date()
```


## Interactive Plot by plotly package (1/2)
- First, I load **plotly package**

```{r package, results='hide', message=FALSE}
library(plotly)
```
- Then, I filter diamonds dataset by carat (from 2 to 3)

```{r filter}
data <- filter(diamonds, carat>2, carat<3)
```
## Interactive Plot by plotly package (2/2)
```{r plot}
plot_ly(data, x= ~price, y = ~carat, color = ~cut, type = "scatter", mode = "markers")
```

##Thank you!!
